Size Convergence of the E$\times$B \\ Staircase Pattern in Flux Tube \\ Simulations of Ion Temperature \\ Gradient-Driven Turbulence

### 2023-06-23 presentation/presentation.tex
#39: Declutter Text on presentation

		\begin{center}
			\begin{itemize}
				\item <2-> Ion temperature gradient-driven turbulence close to marginal stability exhibits Zonal flow pattern formation on mesoscales 
				\item <3-> Patterns are called $\exb$ staircase structures
			\end{itemize}
		\end{center}
		\bigskip
		\onslide<4-> Observed pattern formation in
		\begin{center}
			\begin{itemize}
				\item <5-> local gradient-driven flux-tube simulations, including collisions and background $\exb$ shear,
				\item <6-> local flux-driven realizations, including mean electric field shear,
				\item <7-> global gradient-driven and global flux-driven studies.
			\end{itemize}
			\bigskip
			\onslide<8-> \textbf{Does the basic pattern size always converges to the box size, or is there a typical mesoscale size inherent to staircase structures also in a local flux-tube description?}
		\end{center}
	\end{frame}

@@

	\begin{frame}
		\frametitle{Drift in the Gyrocenter}
		\begin{center}
			\begin{tabular}{>{\onslide<2->}c<{\onslide} >{\onslide<3->}c<{\onslide} >{\onslide<3->}c<{\onslide}}
				{\boldmath $\exb$} \textbf{Drift} & 
				{\boldmath $\nabla B$} \textbf{Drift} & 
				\textbf{Curvature Drift} \\
				$\vect{v}_{E} = \frac{\vect{E}\times\vect{B}}{B^2}$ & 
				$\vect{v}_{\nabla B} = \frac{m v^2_{\perp}}{2 q}\frac{\vect{B}\times \nabla B}{B^3}$ & 
				$\vect{v}_{\kappa} = \frac{m v^2_{\parallel}}{qB^2}\vect{B}\times \underbrace{\vect{\kappa}}_{\frac{\nabla B}{B}} = \frac{m v^2_{\parallel}}{q} \frac{\vect{B}\times \nabla B}{B^3}$\\[1cm]
				\input{../pictures/Theory/ExB-Drift.tex} & 
				\multicolumn{2}{>{\onslide<3->}c<{\onslide}}{\input{../pictures/Theory/GradB-Drift.tex}} \\
			\end{tabular}
		\end{center}

	\end{frame}
	\begin{frame}
		\frametitle{Magnetic Confinement in Tokamak}
		\begin{center}
			\begin{tabular}{>{\onslide<2->}c<{\onslide} >{\onslide<2->}c<{\onslide}}
				\includegraphics[width=0.6\paperwidth]{Theory/Tokamak-Torus.pdf} & $\beta = \frac{nT}{\mu_0 B^2/2}$
			\end{tabular}
		\end{center}
	\end{frame}

@@

		\onslide<3-> Properties:
		\begin{enumerate}
			\item[(1)] <4-> They occur on a \textit{radial mesoscale} of order of $\rho_\mathrm{L} < 10\,\rhoth < R$
			\item[(2)] <5-> The structure are \textit{quasi stationary} in space and vary on time scales much longer than the typical turbulence time scales.
			\item[(3)] <6-> They have a \textit{typical amplitude} of the order of $10^{-1} \vth/R$.
			\item[(4)] <7-> Turbulent transport occurs in \textit{avalanches} with propagation strongly linked to the local $\exb$ shearing rate.
		\end{enumerate}
		\onslide<8->{
		\begin{center}
			\begin{tabular}{c c}
				$\wexb = \frac{1}{2} \frac{\partial^2 \langle \phi \rangle}{\partial \xcoord^2}$ & $\langle \phi \rangle = \frac{1}{L_\ycoord} \int_0^{L_\ycoord} \mathrm{d}\ycoord ~ \phi(\xcoord,\ycoord,s=0)$ \\
			\end{tabular}
		\end{center}
		}
	\end{frame}

@@

		\begin{center}
			\onslide<2-> $\wexb = \sum_{\kzf} \hatwexb(\kzf,t) \, \exp(\mathrm{i} \kzf \xcoord)$ \\[0.5cm]
			\onslide<2-> $\kzf = 2\pi \nzf/L_\xcoord$ \\[0.5cm]
			\onslide<2-> $\hatwexbamp = 2 |\hatwexb(\kzf,t)|$ \\[0.5cm]
			\begin{itemize}
				\item <3-> Zonal flow mode that dominates the $\exb$ staircase pattern are called \textbf{basic mode} 
				\item <4-> The basic mode exhibits the maximum amplitude in the spectrum $\hatwexbamp$
			\end{itemize}
		\end{center}
	\end{frame}
	\begin{frame}
		\frametitle{Restart Script}
		\pause

@@

			\only<12>{\includegraphics[height = 0.5\paperheight]{Comparison/Boxsize/S6_rlt6.0_boxsize3x1-1.5-2.5-3-5_Ns16_Nvpar48_Nmu9_wexb_comparison.pdf}}
		\end{center}

		\only<13>{
			\begin{center}
				$\Rightarrow$ Mesoscale pattern size of: \\[0.3cm]
				$\boxed{\sim 57 - 76\,\rhoth}$ \bigskip
				\begin{itemize}
					\item Non-locality is inherent to ITG-driven turbulence
					\item Avalanches are spatially organized by the E × B staircase pattern
				\end{itemize}
			\end{center}
		}
	\end{frame}

>>>>

		\begin{center}
			\begin{itemize}
				\item <2-> Zonal flow pattern formation on mesoscales in Ion temperature gradient-driven turbulence 
				\item <3-> Patterns are called $\exb$ staircase structures
				\item <4-> Pattern formation observed in \textbf{local/global flux/gradient-driven} studies
			\end{itemize}
		\end{center}
		\bigskip
		\begin{center}
			\begin{itemize}
				\item <5-> \textbf{Global studies:} Multiple radial repetitions of staircase structures with a typical pattern size of several ten Larmor radii
				\item <6-> \textbf{Local studies:} Radial size of $\exb$ staircase structures always converge to the radial box size
			\end{itemize}
			\bigskip
			\onslide<7-> \textbf{Does the basic pattern size always converges to the box size, or is there a typical mesoscale size inherent to staircase structures also in a local flux-tube description?}
		\end{center}
	\end{frame}

@@

	\begin{frame}
		\frametitle{Drift in the Gyrocenter}
		\begin{center}
			\begin{tabular}{>{\onslide<2->}c<{\onslide} >{\onslide<3->}c<{\onslide} >{\onslide<3->}c<{\onslide}}
				{\boldmath $\exb$} \textbf{Drift} & 
				{\boldmath $\nabla B$} \textbf{Drift} & 
				\textbf{Curvature Drift} \\
				$\vect{v}_{E} = \frac{\vect{E}\times\vect{B}}{B^2}$ & 
				$\vect{v}_{\nabla B} = \frac{m v^2_{\perp}}{2 q}\frac{\vect{B}\times \nabla B}{B^3}$ & 
				$\vect{v}_{\kappa} = \frac{m v^2_{\parallel}}{qB^2}\vect{B}\times \underbrace{\vect{\kappa}}_{\frac{\nabla B}{B}} = \frac{m v^2_{\parallel}}{q} \frac{\vect{B}\times \nabla B}{B^3}$\\[1cm]
				\input{../pictures/Theory/ExB-Drift.tex} & 
				\multicolumn{2}{>{\onslide<3->}c<{\onslide}}{\input{../pictures/Theory/GradB-Drift.tex}} \\
			\end{tabular}
		\end{center}
	\end{frame}

	\begin{frame}
		\frametitle{Magnetic Confinement in Tokamak}
		\begin{center}
			\begin{tabular}{>{\onslide<2->}c<{\onslide} >{\onslide<2->}c<{\onslide}}
				\includegraphics[width=0.6\paperwidth]{Theory/Tokamak-Torus.pdf} & $\beta = \frac{nT}{\mu_0 B^2/2}$
			\end{tabular}
		\end{center}
	\end{frame}

@@

		\onslide<3-> Properties:
		\begin{enumerate}
			\item[(1)] <4-> \textit{Radial mesoscale} of order of $\rho_\mathrm{L} < 10\,\rhoth < R$
			\item[(2)] <5-> \textit{Quasi stationary} in space 
			\item[(3)] <6-> Time scales much longer than the typical turbulence time scales
			\item[(4)] <7-> \textit{Typical amplitude} of the order of $10^{-1} \vth/R$.
			\item[(5)] <8-> Turbulent transport strongly linked to the local $\exb$ shearing through \textit{avalanches}
		\end{enumerate}
		\onslide<9->{
		\begin{center}
			\begin{tabular}{c c}
				$\wexb = \frac{1}{2} \frac{\partial^2 \langle \phi \rangle}{\partial \xcoord^2}$ & $\langle \phi \rangle = \frac{1}{L_\ycoord} \int_0^{L_\ycoord} \mathrm{d}\ycoord ~ \phi(\xcoord,\ycoord,s=0)$ \\
			\end{tabular}
		\end{center}
		}
	\end{frame}

@@

		\begin{center}
			\onslide<2-> $\wexb = \sum_{\kzf} \hatwexb(\kzf,t) \, \exp(\mathrm{i} \kzf \xcoord)$ \\[0.5cm]
			\onslide<2-> $\kzf = 2\pi \nzf/L_\xcoord$ \\[0.5cm]
			\onslide<2-> $\hatwexbamp = 2 |\hatwexb(\kzf,t)|$ \\[0.5cm]
			\begin{itemize}
				\item <3-> Zonal flow mode that dominates the staircase pattern are called \textbf{basic mode} 
				\item <4-> The basic mode exhibits the maximum amplitude in the spectrum $\hatwexbamp$
			\end{itemize}
		\end{center}
	\end{frame}
	\begin{frame}
		\frametitle{Restart Script}
		\pause

@@

			\only<12>{\includegraphics[height = 0.5\paperheight]{Comparison/Boxsize/S6_rlt6.0_boxsize3x1-1.5-2.5-3-5_Ns16_Nvpar48_Nmu9_wexb_comparison.pdf}}

			\only<14>{
				\textbf{Does the basic pattern size always converges to the box size, or is there a typical mesoscale size inherent to staircase structures also in a local flux-tube description?}\bigskip

				$\Rightarrow$ Mesoscale pattern size of: \\[0.3cm]
				$\boxed{\sim 57 - 76\,\rhoth}$ \bigskip

				\begin{itemize}
					\item Non-locality is inherent to ITG-driven turbulence
					\item Avalanches are spatially organized by the $\exb$ staircase pattern
				\end{itemize}
			}
		\end{center}
	\end{frame}
